\documentclass[10pt,letterpaper]{article}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
\title{Introductory Quantum Mechanics Homework 1}
\author{Jeremy Chen}
\date{January 15, 2025}
\begin{document}
	\maketitle

\begin{enumerate}[\textbf{Problem \arabic{enumi}.}]
\item Consider a particle subject to a potential energy $V(x) = a|x|$. The one-dimensional time-independent Schrödinger equation for this potential is given by 
$$\frac{d^{2}\psi}{dx^{2}} + \frac{2m}{\hbar^{2}}(E - a|x|)\psi = 0$$
Define $E = \epsilon(\hbar^{2}a^{2}/m)^{1/3}$ and $x = z(\hbar^{2}/ma)^{1/3}$. 
\begin{enumerate}[(a)]
\item Using only symmetry considerations, sketch the lowest three energy eigenstates for a particle bound in this potential. 

\color{violet}
The energy for some $E_{n}$ is $\frac{n^{2}\hbar^{2}\pi^{2}}{2mL^{2}}$. 
\color{black}

\item Show that $\epsilon$ and $z$ are dimensionless. 

\color{violet}
Starting with $z$, position function will be used. Since the dimensions of potential energy is $ML^{2}T^{-2}$, the dimension of $a$ should be $MLT^{-2}$ since potential energy is $a|x|$ and $x$ is $L$. The dimensional representation of $x$ should be the following equality.
$$L = z\left( \frac{(ML^{2}T^{-1})^{2}}{L * MLT^{-2}} \right)^{1/3} = z\left( \frac{M^{2}L^{4}T^{-2}}{M^{2}LT^{-2}} \right)^{1/3} = z(L^{3})^{1/3} = zL $$
As seen above, the simplification would result in the same dimensions on both sides, hence $z$ is dimensionless. Next is the energy eigenfunction, which has dimension $ML^{2}T^{-2}$ and can be represented by the following equality. 
$$ML^{2}T^{-2} = \epsilon \left( \frac{(ML^{2}T^{-1})^{2}(MLT^{-2})^{2}}{M} \right)^{1/3} = \epsilon ( M^{3}L^{6}T^{-6} )^{1/3} = \epsilon ML^{2}T^{-2}$$
Through the simplification, both the left and right hand side have the same dimensions, meaning that $z$ is dimensionless as well. 
\color{black}

\item Show that the Schrödinger equation above can be expressed in the form
$$\frac{d^{2}\psi}{dx^{2}} + 2(\epsilon - |z|)\psi = 0$$

\color{violet}
Substituting the energy eigenfunction and position function into the given Schrödinger equation would result in the following equality.
$$\frac{d^{2}\psi}{dx^{2}} + \frac{2m}{\hbar^{2}}\left[ \epsilon \left( \frac{\hbar^{2}a^{2}}{m} \right)^{1/3} - a\left| z\left( \frac{\hbar^{2}}{ma} \right)^{1/3} \right| \right]\psi = 0$$
Then it could be evaluated for.
\begin{gather*}
\frac{d^{2}\psi}{dx^{2}} + \left( \frac{2m^{2/3}\epsilon a^{2/3}}{\hbar^{4/3}} - \left| \frac{2m^{2/3}a^{2/3}z}{\hbar^{4/3}} \right| \right)\psi = 0 \\
\frac{d^{2}\psi}{dx^{2}} + 2(\epsilon - |z|)\frac{m^{2/3}a^{2/3}}{\hbar^{4/3}}\psi = 0
\end{gather*}
If we were to assume at some point that the potential energy that the particle is subject to is such that $a^{2/3} = \frac{\hbar^{4/3}}{m^{2/3}}$, so the resulting equality would be
$$\frac{d^{2}\psi}{dx^{2}} + 2(\epsilon - |z|)\psi = 0$$
\color{black}

\end{enumerate}
\item Consider the one-dimensional Schrödinger equation with a step potential 
$$U(x) = \begin{cases}
0 & x < -a \\
U_{0} & -a < x < a \\
0 & x > a
\end{cases}$$
where $a$ and $U_{0}$ are positive constants. Using matching conditions at $x = \pm a$, find the transmitted wave function $\psi(x, t)$ and probability density $\rho(x, t)$ in the region $x > a$, for an incident wave corresponding to a particle of mass m and energy $E = U_{0}/2$ moving towards the potential barrier from $x < -a$. Express the results in terms of the quantity $k = \sqrt{2mE/\hbar}$. 

\color{violet}

\color{black}

\item 

\begin{enumerate}[(a)]
\item Show explicitly by matrix multiplication that the Pauli matrices obey
$$\sigma^{i}\sigma^{j} = \delta^{ij}\mathbb{I} + i\epsilon^{ijk}\sigma^{k}$$

\item Prove $[\vec{a} \cdot \vec{\sigma}, \vec{b} \cdot \sigma] = 2i(\vec{a} \times \vec{b}) \cdot \sigma $
\end{enumerate}
\end{enumerate}
\end{document}